Are We Reusing Outdated Code from Stack Overflow?

### 2016-11-04 latex-acm/cloneoverflow.tex
Updated LaTeX

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 130,644,707 clone pairs and manually investigated 2,371 meaningful clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 63 Java open source projects.

@@

\subsection{Experimental Setup}
\subsubsection{Datasets}
\textbf{Stack Overflow}: we extracted 144,075 Java code snippets from accepted answers in a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump is in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We are interested in code snippets embedded in posts. Code snippet is a piece of code located between \texttt{<code></code>} tags. We filtered the snippets with two filtering criteria. First, we ignore snippets that are less than 6 lines since they are usually ignored by clone detection research \cite{something}. Second, we are only interested in code snippets from posts that are marked as ``accepted answer'' since they have high chances to be reused than snippets in questions and other answers. Each snippets is extracted from the dump using regular expressions and stored in a file with post ID as the file's name. We add \texttt{.java} as files' suffix so the clone detectors can recognise them. If a Stack Overflow conversation has more than one code snippet in an accepted answer, we append an indexing number starting from zero behind the ID (e.g. 45051109\_0.java, and 45051109\_1.java).

\textbf{Qualitas corpus}: we selected the latest version (20130901r) of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects. \textit{eclipse} project does not contain source code so it has been removed from the study resulting in totally 63 projects. The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.

\subsubsection{Clone Detectors}
We selected two clone detectors for this study: Simian \cite{simian} and NICAD \cite{Cordy,Roy2008}. There is a few restrictions in terms of choosing clone detection tools for this study. First, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets which are not in a complete block or compilable. This restriction forces us to remove two well-known clone detectors; CCFinder \cite{Kamiya2002}, and DECKARD \cite{Jiang2007a}; from our study since they failed to analyse the complete 144,075 Stack Overflow snippets. Second, since the amount of code that have to be process are large \FIXME{Find SLOC of 144,075 SO snippets and 63 projects}, the clone detector must be scalable enough to execute and report clones in a reasonable amount of time. We found that both Simian and NICAD are able to handle clones in this situation with an acceptable running time.

@@

\section{Results}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stack Overflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from a study by Wang et al.~\cite{Wang2013}. %Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

\begin{table}[H]
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		%		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
		%		\hline
		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ % & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ \hline
		\hline
		\textit{Successful} & 63 & 63 & 57 & 46 \\ %& 44 & 40 & 34 \\
		\textit{Clust.~fail} & - & - & 6 & 13 \\
		\textit{Ren.~fail} & - &  - & 0 & 4 \\
		\hline
		%		& \textit{6 clustering failed} & \textit{13 clustering failed} \\ %& & \textit{4 clustering failed} & \textit{6 clustering failed} \\
		%		& cayenne   & cayenne 	\\ %& & jboss (wildfly) & ArgoUML \\
		%		& checkstyle & checkstyle \\ %& & hadoop & checkstyle \\
		%		& db-derby 	& db-derby 	\\ %& & db-derby & db-derby \\
		%		& geotools 	& geotools  \\ %& & hibernate & cayenne \\
		%		& iReport 	& iReport   \\ %& & & jena \\
		%		& hibernate & ArgoUML 	\\ %& & & geotools \\
		%		&			& castor 		\\ %& & & \\
		%		&			& drjava 		\\ %& & & \\
		%		&			& ganttproject 	\\ %& & & \\
		%		&			& ivatagroupware \\ %& & &  \\
		%		&			& jasperreports \\ %& & & \\
		%		&			& jboss 		\\ %& & & \\
		%		&			& jchempaint 	\\ %& & & \\
		%		\hline
		%		& 			&  \textit{4 renaming failed} \\ %& & & \textit{4 renaming failed} \\
		%		&			& Vuze 		\\ %& & & Vuze \\
		%		&			& aspectj 	\\ %& & & hadoop \\
		%		&			& eXoPortal 	\\ %& & & jboss (wildfly) \\
		%		&			&  hibernate 	\\ %& & & hibernate \\
		%		\hline
	\end{tabular}
\end{table}

@@

			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD \\
			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 \\
			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 \\
			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 \\
			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 \\
			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) \\
			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 \\
			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 \\
			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 \\
			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 \\

@@

			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  \\

@@

			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  \\
			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 \\

@@

			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 \\
			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  \\
			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 \\

@@

			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 \\
			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 \\
			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 \\
			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 \\

@@

			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 \\

@@

			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 \\
			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 \\
			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 \\
			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ \\
			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  \\
			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 \\
			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 \\
			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 \\
			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 \\
			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 \\
			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 \\
			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 \\

@@

			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 \\
			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  \\

@@

			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) \\

@@

			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 \\

@@

			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) \\
			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) \\
			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 \\
			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 \\

@@

			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 \\
			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 \\
			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 \\

@@

@@

Nevertheless,  NiCad produced renaming and clustering errors for some of the settings. This resulted in not all 63 projects had NiCad clone reports. For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors. For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvCl}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs. \FIXME{Report the errors to NiCad creator.}

@@

\begin{table*}
	\centering
	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-match pairs which excludes the subsumed \textit{good}-match and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ pairs.}
	\label{tab:classification_good_o}
	\small
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & \textbf{5} & 5 & 4 & 4 & 26  & 6 & 1320 & \textbf{1352} & 56 & 402 & 31 & \textbf{1357} & 61 & 406 & 32 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 23  & 8 & \textbf{39} & 8 & 9 & 6 & 480 & 28 & 61 & \textbf{569} & 76 & 60 & 16 & \textbf{608} & 83 & 68 & 19 \\
		\hline
	\end{tabular} 
\end{table*}

%\begin{table}
%	\centering
%	\caption{Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
%	\label{tab:classification}
%	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{5mm}|R{3mm}|R{7mm}|R{7mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{7mm}|R{3mm}|R{7mm}|R{7mm}|}
%		\hline
%		\multirow{2}{*}{Classification}	& \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ 	\cline{2-17}
%		 & A & A' & B & C & D & E & F & Total 
%		 & A & A' & B & C & D & E & F & Total \\ 
%		\hline 
%		\multirow{1}{*}{\textit{good-match(0.7)}} 
%		& 1 & 0 & 1  & 3 & 26  & 6 & 1,369 & 1,406 
%		& -- & -- & -- & -- & -- & -- & -- & --  \\ \cline{2-8}
%		\hline
%		\multirow{1}{*}{\textit{ok-match(0.7)}} 
%		& 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 
%		& 2 & 0 & 0 & 0 & 6,676 & 1 & 27 & 6,706 \\ \cline{2-8}
%		\hline
%		TP/FP
%		& \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070
%		& \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{6,704} & 6,706 \\ 
%		\hline
%		Unique SO fragments & \multicolumn{4}{c|}{10} & & & & & \multicolumn{4}{c|}{1} & & & & \\
%		\hline
%		Unique Q files & \multicolumn{4}{c|}{13} & & & & & \multicolumn{4}{c|}{1} & & & & \\
%		\hline
%		Unique Q projects & \multicolumn{4}{c|}{8} & & & & & \multicolumn{4}{c|}{1} & & & & \\
%		\hline
%	\end{tabular} 
%\end{table}

\begin{table}
	\centering
	\caption{Distribution of classification category A--F according to \textit{good}- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
	\label{tab:good_classification}
	\small
	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
		\hline 
		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
		\hline
		\hline
		\multicolumn{9}{|c|}{\textit{good}-match pairs} \\
		\hline
		S$_{df}$--N$_{df}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
		S$_{\textrm{\textit{EvCl}}}$--N$_{\textrm{\textit{EvCl}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1319 & 1338 \\
		\hline
		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1320  & 1366 \\
		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1320  & 1352 \\
		\hline
		\hline 
%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
%		\hline
		\multicolumn{9}{|c|}{\textit{ok}-match pairs} \\
		\hline
		S$_{df}$--N$_{df}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   	& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   	& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
		\hline
		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
		\hline
	\end{tabular} 
\end{table}

>>>>

\FIXME{Add motivating example here}

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 266,837,480 similar code fragment pairs and manually investigated x,xxx candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 109 Java open source projects.

@@

\subsection{Experimental Setup}
\subsubsection{Datasets}
\textbf{Stack Overflow}: we extracted 144,075 Java code snippets from accepted answers in a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump is in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We are interested in code snippets embedded in posts. Code snippet is a piece of code located between \texttt{<code></code>} tags. We filtered the snippets with two filtering criteria. First, we ignore snippets that are less than 6 lines since they are usually ignored by clone detection research \cite{something}. Second, we are only interested in code snippets from posts that are marked as ``accepted answer'' since they have high chances to be reused than snippets in questions and other answers. Each snippets is extracted from the dump using regular expressions and stored in a file with post ID as the file's name. We add \texttt{.java} as files' suffix so the clone detectors can recognise them. If a Stack Overflow conversation has more than one code snippet in the accepted answer, we append an indexing number starting from zero behind the ID (e.g. 45051109\_0.java, and 45051109\_1.java).

\textbf{Qualitas corpus}: we selected the latest version (20130901r) of Qualitas corpus \cite{QualitasCorpus} containing 112 Java open source projects. Three projects (\textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}) do not contain source code so it has been removed from the study resulting in totally 109 projects. Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

\subsubsection{Clone Detectors}
We selected two clone detectors for this study: Simian \cite{simian} and NICAD \cite{Cordy,Roy2008}. There is a few restrictions in terms of choosing clone detection tools for this study. First, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods. Hence, the tool must be flexible enough to process code snippets which are not in a complete block or compilable. This restriction forces us to remove two well-known clone detectors; CCFinder \cite{Kamiya2002}, and DECKARD \cite{Jiang2007a}; from our study since they failed to analyse the complete 144,075 Stack Overflow snippets. Second, since the amount of code that have to be process are large \FIXME{Find SLOC of 144,075 SO snippets and 109 projects}, the clone detector must be scalable enough to execute and report clones in a reasonable amount of time. We found that both Simian and NICAD are able to handle clones in this situation with an acceptable running time.

@@

\section{Results}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stack Overflow fragments (Java accepted answers) and 109 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using two different settings: default settings, and settings from a study by Wang et al.~\cite{Wang2013}. %Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

\begin{table}[H]
	\centering
	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		%		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
		%		\hline
		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ % & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ \hline
		\hline
		\textit{Successful} & 109 & 109 & 97 & 82 \\ %& 44 & 40 & 34 \\
		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
		\textit{Renm.~fail} & -- &  -- & -- & 11 \\
		\hline
		%		& \textit{6 clustering failed} & \textit{13 clustering failed} \\ %& & \textit{4 clustering failed} & \textit{6 clustering failed} \\
		%		& cayenne   & cayenne 	\\ %& & jboss (wildfly) & ArgoUML \\
		%		& checkstyle & checkstyle \\ %& & hadoop & checkstyle \\
		%		& db-derby 	& db-derby 	\\ %& & db-derby & db-derby \\
		%		& geotools 	& geotools  \\ %& & hibernate & cayenne \\
		%		& iReport 	& iReport   \\ %& & & jena \\
		%		& hibernate & ArgoUML 	\\ %& & & geotools \\
		%		&			& castor 		\\ %& & & \\
		%		&			& drjava 		\\ %& & & \\
		%		&			& ganttproject 	\\ %& & & \\
		%		&			& ivatagroupware \\ %& & &  \\
		%		&			& jasperreports \\ %& & & \\
		%		&			& jboss 		\\ %& & & \\
		%		&			& jchempaint 	\\ %& & & \\
		%		\hline
		%		& 			&  \textit{4 renaming failed} \\ %& & & \textit{4 renaming failed} \\
		%		&			& Vuze 		\\ %& & & Vuze \\
		%		&			& aspectj 	\\ %& & & hadoop \\
		%		&			& eXoPortal 	\\ %& & & jboss (wildfly) \\
		%		&			&  hibernate 	\\ %& & & hibernate \\
		%		\hline
	\end{tabular}
\end{table}

@@

			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD & \\
			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 & \\
			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 & \\
			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 & \\
			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 & \\
			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) & \\
			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 & \\
			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\

@@

			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\

@@

			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  & \\
			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 & \\

@@

			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 & \\
			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  & \\
			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 & \\

@@

			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 & \\
			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 & \\

@@

			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 & \\

@@

			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 & \\
			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 & \\
			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ & \\
			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 & \\
			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 & \\
			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 & \\
			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 & \\
			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 & \\

@@

			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 & \\
			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\

@@

			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\

@@

			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 & \\

@@

			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) & \\
			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 & \\
			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\

@@

			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 & \\
			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\

@@

\begin{table*}
	\centering
	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
	\label{t:new_and_old}
	%	\resizebox{\columnwidth}{!}{%
	\small
	\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
		\hline 
			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
			\hline
			apache-jmeter & 2. 9 & & & & & \\
			apache-log4j & 1.2.16 & & & & & \\
			apache-maven & 3.0 & & & & & \\
			apache-roller & 4.0.1 & & & & & \\
			apache-tomcat & 7.0.2 & & & & & \\
			jhotdraw & 7.5.1 & & & & & \\
			jrefactory & 2.9.19 & & & & & \\
			jruby & 1.5.2 & & & & & \\
			jspwiki & 2.8.4 & & & & & \\
			jstock & 1.0.7c & & & & & \\
			jsxe & 04\_beta & & & & & \\
			jtopen & 7\_1 & & & & & \\
			jung2 & 2\_0\_1 & & & & & \\
			lucene & 4.3.0 & & & & & \\
			marauroa & 3.8.1 & & & & & \\
			megamek & 0.35.18 & & & & & \\
			mvnforum (mvnad) & 1.2.2 (1.0.1) & & & & & \\
			myfaces-core & 2.0.2 & & & & & \\
			nakedobjects & 4.0.0 & & & & & \\
			nekohtml & 1.9.14 & & & & & \\
			netbeans & 6.9.1 & & & & & \\
			openjms & 0.7.7-beta-1 & & & & & \\
			oscache & 2.4.1 & & & & & \\
			picocontainer & 2.10.2 & & & & & \\
			pmd & 4.2.5 & & & & & \\
			poi & 3.6 & & & & & \\
			pooka & 080505 & & & & & \\
			proguard & 4.5.1 & & & & & \\
			quartz & 1.8.3 & & & & & \\
			quickserver & 1.4.7 & & & & & \\
			quilt & 0.6-a-5 & & & & & \\
			rssowl & 2.0.5 & & & & & \\
			sablecc & 3.2 & & & & & \\
			sandmark & & & & & & \\
			spring-framework & 3.0.5 & & & & & \\
			struts2 & 2.2.1-all & & & & & \\
			sunflow & 0.07.2 & & & & & \\
			tapestry & 5.1.0.5 & & & & & \\
			trove & 2.1.0 & & & & & \\
			velocity & 1.6.4 & & & & & \\
			wct-package & 1.5.2 & & & & & \\
			webmail & 0.7.10 & & & & & \\
			weka & 3-7-9 & & & & & \\
			xalan-j & 2\_7\_1 & & & & & \\
			xerces-J & 2.10.0 & & & & & \\
			xmojo & 5.0.0 & & & & & \\
			\hline 
		\end{tabular} %
%	}
\end{table*}

@@

Nevertheless,  NiCad produced renaming and clustering errors for some of the settings. This resulted in not all 109 projects had NiCad clone reports. For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors. For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvCl}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs. \FIXME{Report the errors to NiCad creator.}

@@

\begin{table*}
	\centering
	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-match pairs which excludes the subsumed \textit{good}-match and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ pairs.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
		\hline
		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
		\hline 
		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 33  & 8 & \textbf{49} & 12 & 14 & 10 & 4459 & 35 & 82 & \textbf{4576} & 99 & 136 & 29 & \textbf{4625} & 110 & 150 & 33 \\
		\hline
	\end{tabular} 
}
\end{table*}

%\begin{table}
%	\centering
%	\caption{Distribution of classification category A--F according to \textit{good}- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
%	\label{tab:good_classification}
%	\small
%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
%		\hline 
%		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
%		\hline
%		\hline
%		\multicolumn{9}{|c|}{\textit{good}-match pairs} \\
%		\hline
%		S$_{df}$--N$_{df}$   & 1 & 0 & 1 & 0 & 1 & 4 & 0 & 7 \\
%		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   & 1 & 0 & 0 & 3 & 14 & 1 & 1 & 20 \\
%		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   & 0 & 0 & 3 & 0 & 7 & 0 & 0 & 10 \\
%		S$_{\textrm{\textit{EvCl}}}$--N$_{\textrm{\textit{EvCl}}}$   & 0 & 0 & 1 & 0 & 20 & 0 & 2188 & 2228 \\
%		\hline
%		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1320  & 1366 \\
%		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1320  & 1352 \\
%		\hline
%		\hline 
%%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
%%		\hline
%		\multicolumn{9}{|c|}{\textit{ok}-match pairs} \\
%		\hline
%		S$_{df}$--N$_{df}$        & 3 	& 0 	& 12	& 6 	& 3755  & 8	& 7  &  3791 \\
%		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   	& 8 	& 0 	& 28	& 4	& 904 & 29  & 32 &  1005 \\
%		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   	& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
%		\hline
%		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
%		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
%		\hline
%	\end{tabular} 
%\end{table}
